A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-02-22 article.tex
润色后的文献第一稿

\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers}

\author[hust,ncst]{Lei Zhang}
\ead{zhanglei@ncst.edu.cn}	
\author[hust]{Tao Yang\corref{cor1}}
\ead{hust\_yt@hust.edu.cn}

\address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074,China}
\address[ncst]{College of Metallurgy and Energy, NorthChina University of Science and and Technology, Tangshan 063009,China}
\cortext[cor1]{Corresponding authors}

\begin{abstract}%修改到300字以内
Double-reheat ultra-supercritical (USC) unit has received extensive attention for its high efficiency and energy-saving effect.
The optimal design of its thermal system is still under study.
Herein, an optimized system for reasonable fluid heat transfer temperature matching and higher efficiency was proposed.
The novel system used turbine extractions as heat sources of air preheaters and low-pressure economizers to absorb economizer outlet flue gas’ heat, which realized the join optimization of air preheat process and regenerative system.
Models were built to compare energetic performance of the novel system and reference system.
In addition, thermodynamic analyses under partial load operation conditions was conducted. 
Exergy analysis method was used to identify exergy destruction changes of transformed parts and analyze the cause of the change.
Result shows the novel system can largely decrease exergy destruction rate of air preheat process and improve the system's thermal performance.
Furthermore, the novel system increases the temperature of secondary air and reduces the overall superheat degree of several extractions.
Theoretically, the novel system with a overall exergy efficiency of 48.73\%  and reduces the SCE consumption by nearly 5.5\,g/kWh under THA load when the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
Moreover, the novel system can still has advantages in coal saving under partial load condition.
Results indicate that the novel system could improves the performance of double-reheat USC unit and may provide a theoretical basis for its optimization.

@@

\begin{keyword}
Double reheat \sep Ultra-supercritical power plant \sep Exergy analysis \sep air preheat process \sep Thermodynamic analyses
\end{keyword}

@@

\section{Introduction}
\label{sec1:intro}
Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
Statics show that China has been the largest producer and consumer of energy all over the world since 2013~\cite{Petroleum2014BP}. 
For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
Improve system efficiency and reducing coal consumption is still the main task of power plant design. Nowadays, ultra-supercritical (USC) power plants with large capacity and high parameter are considered to be feasible means to save energy and have rapidly developed word-wide.
The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
According to Ref.~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
 Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
 Since 2012, five  double reheat USC units  began to build in China, and three of them put it into operation in 2015.
 Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world.

Though the high live steam pressure and temperature of USC unit improves its efficiency, there are still some imperfections which limit the improvement of its performance . 
In order to make an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
It pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.

Compared with common USC system, double-reheat system has some characteristic problems, such as double reheat ratio chose and great superheat degree of the first several extractions.
And some common problems, such as the high boiler exhaust temperature, which leads to unreasonable energy-level matching and great exergy destruction.

To chose a reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out parametric analysis and system optimization in double reheat ultra-supercritical power plants based on exergy analysis and economic analysis. The result shows reasonable reheat parameters and reheat stage number can improve  double reheat system's performance.

To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with single reheat after the installation of an additional outer steam cooler (AOC).
Results show that the AOC is an effective method to reduce the superheat degree and improve the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system adopting 10-stage extractions and two outer steam coolers. 
The result of thermodynamic and techno-economic analyses shows this system can reduce cost of electricity to 55.89 USD/MWh.
Besides, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine to utilize the superheat degree of the extractions.
In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine not the regenerative heater.
Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design, and the exergy destruction of regenerative heaters is reduced, which results in an overall improvement in efficiency.

To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low pressure economizer (LPE) based on the data of some 1000\,MW typical power generation units in China and four possible arrangements of the LPE installation were proposed to compare its energy-saving effects.
Results indicated that LPE connected with higher temperature section of the condensate line brings more reduction of standard coal equivalent (SCE).
Wang et al.~\cite{Wang2012Application} investigated the energy and water saving and the reduction of CO$_2$ after the installation of LPE.
Results show that the optimized measures can bring a reduction of SCE by 2-4\,g/kWh.
Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high pressure economizer installed at a long term running lignite-fired power plant.
Results show that more than 30\,MW of the flue gas waste heat is recovered, which brings an improvement in gross efficiency by 0.53\% and 9.4\,MW extra output power.
Xu et al~\cite{Xu2013A} made the air preheater divided into two stages to reduce the temperature difference in heat transfer process.
Besides, a LPE is installed between the two air preheaters to obtain an appropriate flue gas temperature range.
Thermodynamic and Technic-economic analysis are conducted to reveal the performance improvement.
It was found that the SCE consumption can be reduced by 6.7\,g/kWh.

Due to  boiler design and thermal system design belong to deferent research area, boiler has been studied as a whole and ignored the joint optimization of boiler heat transfer process and regenerative process.

In this paper, a novel system based on a 1000\,MW double reheat USC reference system  is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized reasonable temperature matching of flue gas, air, extraction steam and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
Specifically, the main works of this study include: (1)Modeling the novel system and reference system with EBSILON® Professional; (2) Using exergy analysis to compare both systems' exergy efficiency , exergy destruction distribution and subsystems performance change;(3) Analyzing both systems' thermal performance under off-design conditions.

\section{System optimization of double reheat USC system}
\label{sec2:system intro}
\subsection{Reference system on operation} % (fold)
\label{sub2:ref intro}
A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
The parameter settings at maximize continuous power are 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure~\cite{Zhao2017Exergy}.
The output power of the reference system under the design condition is 1000 MW.
The unit consists of one super high pressure cylinder (VHP), one high pressure cylinder (HP), one intermediate pressure cylinder (IP), and two low pressure cylinders (LPs).
Regenerative system with four high pressure regenerative heaters (HRHs), five low pressure regenerative heaters (LRHs), and one deaerator (DEA) are adopted.
Besides, two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree. The exhaust steam pressure of the steam turbine is set 4.5\,kPa. The simplified schematic of it is presented in Fig~\ref{fig:reference_system}.

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
The system's boiler heat transfer surfaces arrangement is shown in Fig~\ref{fig:boiler_surface}. 
The boiler furnace is composited by the membrane wall, along flue gas flow direction lays low-temperature superheater (Lts) screen tube, cold segment of high-temperature first reheater (Csf), cold segment of high-temperature second reheater (Css), High temperature super-heater (Hts), hot segment of high-temperature first reheater (Hsf), hot segment of high-temperature second reheater (Hss).
After Hsf and Hss the flue gas channel is divided into the front-duct flue and the back-duct flue.
The front duct arranges low-temperature first reheater (Ltfr) and the front-duct economizer (Feco).
The back duct arranges low-temperature second reheater (Ltsr) and the back-duct economizer (Beco).
(air preheater)APH is arranged in vertical shaft.

From the arrangement of heating transfer surfaces, the boiler can be divided into two parts: the part achieving heat absorption of water/steam process in the furnace, and the APH to complete the air preheat process.
It can be seen that most heating surfaces of boiler is arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
So the horizontal flue and vertical shaft have sufficient space to install other equipments.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/boiler_surface.png}
\caption{Boiler heat transfer surfaces layout} 
\label{fig:boiler_surface}
\end{figure}

@@

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}

Table~\ref{tab:reheater parameter} gives the temperature profiles of regenerative heaters and the air preheater, revealing their energy match level.
For the APH, the temperature of flue gas at the inlet is 376$^\circ$C under, while the temperature of the air to be heated by the flue is 23$^\circ$C.
The logarithm mean temperature difference (LMTD) of the APH is calculated to be 72$^\circ$C.
Compared with the air preheater, the regenerative heaters have much lower LMTD from 6.88$^\circ$C-15.87$^\circ$C.
According to the second law of thermodynamics, the bigger the temperature difference the greater the irreversible loss.
So it needs to optimize the air preheat process to reduce energy loss of the system.
AOC1 and AOC2 face the same problem of high LMTD compared with RHs.
It's better to find a way to make double reheat USC system's high temperature extractions a reasonable arrangement.

\begin{table}[htbp]
\caption{Fluid parameters of regenerative heaters and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.2cm}{LMTD ($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\subsection{Proposal of a novel system with EAPHs and LPEs}
\label{sub2:prop novel sys}

To reduce the energy loss caused by APH, a novel system is proposed, in which air is not heated by flue gas in the conventional air preheater, but 8 turbine-extraction-heated air preheaters (EAPH1-EAPH8).
The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.

As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam divides into two parts, one is sent to the regenerative heater to heat the condensate or feedwater and the other one is sent to corresponding EAPH to heat air.
The drainage from the air preheater joins with that of corresponding regenerative heater after finishing heat transfer .
Steam distribution ratio is determined according to EAPH upper terminal temperature difference settled in the system.
It should be mentioned that not all the extractions are available for air heating.
The last two stage extractions' pressure are much lower than barometric pressure which has a great risk of air leakage into the steam, and APH8 shall be shut down under low load for the same reason.

The AOCs in the reference system are designed to heat feedwater.
Although AOC inlet steam has a great supper heat degree, the small heat exchanged makes feedwater have little temperature rise.
So the LMTD is very high in AOCs.

To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers, four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
Air side outlet of EAPH1 will sent to boiler as secondary air, which has small mass quantity and lower heat capacity compared with feedwater. 
So the secondary air temperature can make a remarkable rise, and LMTD of AOCs can get down.
Extractions from the 2nd to the 5th have very high temperature and great superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air respectively.

@@

Cause removing of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively. 
Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with corresponding regenerative heater's outlet water. 
Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set 95$^\circ$C.

% \section{Model establishment and thermodynamic evaluation} % (fold)
% \label{sec3:modle est and eval}
\section{Model description and Thermodynamic metric}
\label{ssub:model_establishment_and_system_analysis_method}

\subsection{Model establish method and main assumption}
\label{ssub3:modle description}
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
%添加模型中基本部件的特性 添加个表格
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional.
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities and widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
While use this software simulating systems, main equipments work flow parameters and some basic properties need to be settled.
Cause designed based on the reference system, the novel system's main input parameters(such as live steam parameters, fist/second reheat steam parameters and turbine extractions parameters) keeps the same as it, which can be find in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
Based on the practice, the upper temperature differences of novel systems' LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C and 5$^\circ$C. 
And other main components model details are give in Table~\ref{table:model_details}.

>>>>

\title{A novel 1000\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers}

\author[hust,ncst]{Lei Zhang}
\ead{zhanglei@ncst.edu.cn}	
\author[hust]{Jiayi Zhao}
\author[hust]{Tao Yang\corref{cor1}} %I am not sure how to delete the extra comma after Yang's name--there is a comma after the "a" superscript that needs to be removed.
\ead{hust\_yt@hust.edu.cn}	
\author[hust]{Yanping Zhang}
\author[hust]{Wei Gao}

\address[hust]{School of Energy and Power Engineering, Huazhong University of Science and Technology, Wuhan 430074, China}
\address[ncst]{College of Metallurgy and Energy, North China University of Science and Technology, Tangshan 063009, China}
\cortext[cor1]{Corresponding author}

\begin{abstract}%修改到300字以内
The double-reheat ultra-supercritical (USC) unit has received significant attention because of its high efficiency and energy-saving effects.
The optimal design of the unit's thermal system is still under consideration, however.
In this paper, an optimized system for reasonable fluid heat transfer temperature-matching and higher efficiency is proposed.
This novel system uses turbine extractions as heat sources for air preheaters and low-pressure economizers to absorb economizer outlet flue gas heat, thereby realizing the joint optimization of the air preheat process and the regenerative system.
Models were built to compare the energetic performance of the novel system and that of the reference system.
In addition, thermodynamic analyses under partial load operation conditions were conducted. 
Exergy analysis was used to identify the exergy destruction changes of the transformed parts and to analyze the cause of the changes.
The results show that the novel system largely decreased the exergy destruction rate of the air preheat process and improved the system's thermal performance.
Furthermore, the novel system increased the temperature of secondary air and reduced the overall superheat degree of several extractions.
Theoretically, with an overall exergy efficiency of 48.73\%, the novel system can reduce SCE
%I don't think the "SCE" acronym has been introduced yet. Write it out in full here? 
consumption by nearly 5.5\,g/kWh under the THA load
%Same for THA---write out in full?
if the temperature of the flue gas entering the electrostatic precipitator is set to 95$^\circ$C.
Moreover, the novel system has advantages for coal-saving under the partial load condition.
Ultimately, the results indicate that the novel system can improve the performance of the double-reheat USC unit and may provide a theoretical basis for its optimization.

@@

\begin{keyword}
Double-reheat \sep ultra-supercritical power plant \sep exergy analysis \sep air preheat process \sep thermodynamic analysis
\end{keyword}

@@

\section{Introduction}
\label{sec1:intro}
Coal is still the main fossil fuel resource for the production of electricity globally, according to~\cite{Ouedraogo2013Energy}. 
In China, coal–fired power generation accounts for more than 70\% of the total electricity generation and subsequently contributes almost 50\%, 37\%, 33\%, and 55\% to the SO$_X$, NO$_X$, dust, and CO$_X$ emission volumes, respectively~\cite{Zhang2010Analysis}.
Statistics show that China has been the largest producer and consumer of energy worldwide since 2013~\cite{Petroleum2014BP}. 
In 2016, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%~\cite{Petroleum2017BP}. 
Improving system efficiency and reducing coal consumption remain the primary tasks to be considered in power plant design. Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
According to~\cite{Zhao2017Exergy}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
 Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
 The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
 Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance. 
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion.
%largest proportion of what? Of exergy destruction overall?

Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.

To identify reasonable reheat parameters, Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.

To reduce the superheat degree of the extractions, Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a single reheat after the installation of an additional outer steam cooler (AOC).
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and techno-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the high pressure turbine enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the intermediate pressure turbine are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.

To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China. Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greater reduction in the standard coal equivalent (SCE). %"greatest"? 
Wang et al.~\cite{Wang2012Application} investigated energy- and water-saving measures and the reduction of CO$_2$ after the installation of an LPE.
The results showed that the optimized measures can reduce SCE by 2-4\,g/kWh.
Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high-pressure economizer installed at a long-term running lignite-fired power plant.
The results showed that more than 30\,MW of the flue gas waste heat was recovered, creating an improvement in gross efficiency of 0.53\% and 9.4\,MW extra output power.
Xu et al.~\cite{Xu2013A} divided the air preheater into two stages to reduce the temperature difference in the heat transfer process.
%"divided the air preheater process"? Or was the preheater itself actually divided?
A LPE was also installed between the two air preheaters to obtain an appropriate flue gas temperature range.
Thermodynamic and technic-economic analyses were conducted to reveal the performance improvement.
It was found that the SCE consumption was reduced by 6.7\,g/kWh. %"techno-economic" is used earlier in the paper. Which expression is correct?

The installation of an LPE has some other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.

Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.

In this paper, a novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and LPEs.
Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.

\section{Optimization of the double-reheat USC system}
\label{sec2:system intro}
\subsection{Reference system in operation} % (fold)
\label{sub2:ref intro}
A typical coal-fired double-reheat USC power plant in operation was chosen as the reference unit.
The parameter settings at maximum continuous power were 310\,bar/600$^\circ$C for the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of single-reheat steam pressure to main steam pressure, and 33\% for the proportion of double-reheat steam pressure to single-reheat steam pressure~\cite{Zhao2017Exergy}.
The output power of the reference system under the design condition was 1000 MW.
The unit consisted of one super-high pressure cylinder (VHP), one high-pressure cylinder (HP), one intermediate-pressure cylinder (IP), and two low-pressure cylinders (LPs).
A regenerative system with four high-pressure regenerative heaters (HRHs), five low-pressure regenerative heaters (LRHs), and one deaerator (DEA) was adopted.
In addition, two additional outer steam coolers (AOC1, AOC2) were used to cool two extractions due to their high super-heat degree. The exhaust steam pressure of the steam turbine was set to 4.5\,kPa. Its simplified schematic is presented in Fig.~\ref{fig:reference_system}.

\begin{figure}[htbp]
\centering
\includegraphics[width=1\textwidth]{fig/reference_system}
\caption{Schematic of the reference system} 
\label{fig:reference_system}
\end{figure}
%从参考系统的锅炉虽然仍然采用Π型布置，但其内部受热面和传统一次再热锅炉有较大区别。
The system's boiler heat transfer surface arrangement is shown in Fig.~\ref{fig:boiler_surface}. 
The boiler furnace is composed of the membrane wall; along the flue gas flow direction lie the low-temperature superheater (Lts) screen tube, the cold segment of the first high-temperature reheater (Csf), the cold segment of the second high-temperature reheater (Css), the high-temperature super-heater (Hts), the hot segment of the first high-temperature reheater (Hsf), and the hot segment of the second high-temperature reheater (Hss).
After Hsf and Hss, the flue gas channel is divided into the front-duct flue and the back-duct flue.
The front duct arranges the first low-temperature reheater (Ltfr) and the front-duct economizer (Feco).
The back duct arranges the second low-temperature reheater (Ltsr) and the back-duct economizer (Beco).
The air preheater (APH) is arranged in the vertical shaft. %What does "arranges" mean in these sentences?

From the arrangement of the heating transfer surfaces, the boiler can be divided into two parts: the part performing the heat absorption for the water/steam process in the furnace and the APH that completes the air preheat process.
It can be seen that most heating surfaces of the boiler are arranged in the furnace, while the horizontal flue and vertical shaft are only equipped with APH.
This means that the horizontal flue and vertical shaft leave sufficient space for the installation of other equipment.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/boiler_surface.png}
\caption{Boiler heat transfer surface layout} 
\label{fig:boiler_surface}
\end{figure}

@@

\begin{table}[htbp]
\caption{Main input parameters of the reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}

Table~\ref{tab:reheater parameter} gives the temperature profiles of the regenerative heaters and the air preheater, revealing their energy match level.
For the APH, the temperature of the flue gas at the inlet is less than 376$^\circ$C,  
 while the temperature of the air to be heated by the flue is 23$^\circ$C.
The logarithm mean temperature difference (LMTD) of the APH is calculated as 72$^\circ$C.
Compared with the air preheater, the regenerative heaters have much lower LMTDs, ranging from 6.88$^\circ$C-15.87$^\circ$C.
According to the second law of thermodynamics, the greater the temperature difference, the greater the irreversible loss.
Therefore, the air preheat process needs to be optimized to reduce the energy loss of the system.
AOC1 and AOC2 have the same problem of high LMTDs compared with RHs.
It is important to determine how to make the double-reheat USC system's high temperature extractions a reasonable arrangement.

\begin{table}[htbp]
\caption{Fluid parameters of regenerative heaters and air preheater} %Should "air preheater" be plural here?
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.2cm}{LMTD ($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\subsection{Proposal for a novel system with EAPHs and LPEs}
\label{sub2:prop novel sys}

To reduce the energy loss caused by APH, a novel system is proposed in which air is not heated by flue gas in the conventional air preheater. Rather, eight turbine-extraction-heated air preheaters (EAPH1-EAPH8) are used.
The layout of the optimization system is presented in Fig.~\ref{fig:novel_system}.

As shown in Fig.~\ref{fig:extraction_heat_APH}, the extracted steam is divided in half, with one half sent to the regenerative heater to heat the condensate or feedwater and the other half sent to the corresponding EAPH to heat the air.
The drainage from the air preheater joins with that of the corresponding regenerative heater after the heat transfer has been completed.
The steam distribution ratio is determined according to the EAPH upper terminal temperature difference settled in the system.
It should be noted that not all of the extractions are available for air heating.
The last two stage extractions' pressure values are much lower than their barometric pressure values, which suggests a great risk of air leakage into the steam. APH8 must be shut down under low load for the same reason.

The AOCs in the reference system are designed to heat feedwater.
Although AOC inlet steam has a great supper heat degree %superheat?
, the small amount of heat exchanged makes the feedwater's temperature rise only slightly.
The LMTD is very high in AOCs.

To reduce rise AOCs' exergy efficiency and the superheat degree of extractions entering the heat exchangers,
%Here do you mean to "reduce the possibility of an increase in AOCs'..."?
four additional outer steam coolers (AOC1-AOC4) are installed at the air side outlet of EAPH1.
The air side outlet of EAPH1 is sent to the boiler as secondary air, which has a smaller mass and lower heat capacity compared with the feedwater. 
The secondary air temperature thus can increase remarkably, while the LMTD of AOCs can decrease.
The second through the fifth extractions have very high temperatures and great superheat degrees; they are sent to the AOCs in the order of their temperature levels.
For example, the second extraction has the highest temperature and is applied to heat the air in the first AOC. Then the cooled steam from AOC1 is sent to HRH2 and air EAPH2 to heat the water and air, respectively.  %Should "air EAPH2" be simply "EAPH2"?

@@

Because of the removal of the APH originally installed in the vertical shaft, the flue gas's heat needs to be absorbed by other means.
As shown in Fig.~\ref{fig:novel_system}, the flue gas at the outlet of the economizer is utilized by four LPEs to heat the condensate and feedwater; these LPEs are parallel to HRH2, HRH4, LRH6, and LRH8, respectively. %Rather than "are parallel to," perhaps "correspond with"? 
Part of the condensate and feedwater at the inlet of the regenerative heater is sent to the LPE; then the heated water joins with the corresponding regenerative heater's outlet water. 
Given the acid dew point temperature, the flue gas temperature at the outlet of the last LPE can be set to 95$^\circ$C.

% \section{Model establishment and thermodynamic evaluation} % (fold)
% \label{sec3:modle est and eval}
\section{Model description and thermodynamic metrics}
\label{ssub:model_establishment_and_system_analysis_method}

\subsection{Model establishment method and main assumptions}
\label{ssub3:modle description}
%对模型中如何基于现有系统进行的改造，和哪些数据不发生变化进行说明
%添加模型中基本部件的特性 添加个表格
In this paper, the thermodynamic cycle of the thermal system under different loads is simulated using EBSILON® Professional.
EBSILON is a power plant simulation tool that can calculate thermodynamic quantities. It is widely used in power plant system model establishment and analysis~\cite{Li2015Integrated,Yao2017Multi}. 
The simulation model yields detailed data with a high degree of reliability in calculating the thermodynamic state.
When using this software simulation system, the main equipment's work flow parameters and some basic properties need to be settled.
Because it is designed based on the reference system, the novel system's main input parameters (such as live steam parameters, first/second reheat steam parameters, and turbine extraction parameters) remain the same as those that are shown in Table~\ref{tab:ref input} and Table~\ref{table:extractions_parameter}.
Based on the practice,
%What is "the practice"? 
the upper temperature differences of the novel system's LPE, AOC and EAPH are settled to 30$^\circ$C, 20$^\circ$C, and 5$^\circ$C. 
The details of the model's other main components are given in Table~\ref{table:model_details}.
